\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, nicefrac, enumerate}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\title{Differential equations exam 2 - SP 17}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Exam 2}}
            \hfill MAT 265, Spring 2017}
\bigskip
\bigskip

\begin{questions}

\question[20]
A tank initially contains 1000 liters of pure water.  A solution containing 0.05 kilograms of salt per liter is pumped into the tank at a rate of 5 liters per minute.  A second solution containing 0.04 kilograms of salt per liter is pumped into the tank at a rate of 10 liters per minute.  The well-mixed solution is drained from the tank at a rate of 15 liters per minute.  How many kilograms of salt are in the tank after one hour?

\clearpage


\question[5]
On the interval $I = (0,\infty)$, two solutions of the differential equation 
\begin{align*}
	x^2 y^{\prime \prime} -xy^{\prime} + y = 0
\end{align*}
are the functions
\begin{align*}
	y_1(x) & = x, & y_2(x) & = x \ln x.
\end{align*}

\begin{parts}
\part
Use the Wronskian to show that these solutions are linearly independent on $I$.

\vspace{\stretch{2}}

\part
Give the general solution to the differential equation.
\end{parts}

\vspace{\stretch{2}}

\question[20]
Find the general solution for the following homogeneous problems.

\begin{parts}
\part
$4y^{\prime \prime} + 12y^{\prime} + 9y = 0$

\vspace{\stretch{4}}

\clearpage

\part
$y^{\prime \prime} + 6y = 0$

\vspace{\stretch{2}}

\part
$2y^{\prime \prime} + 2y^{\prime} + y = 0$

\vspace{\stretch{2}}

\part
$y^{\prime \prime} - 3y^{\prime} - 10y = 0$
\end{parts}

\vspace{\stretch{3}}

\clearpage

\question
Find the solution to each differential equation or IVP.

\begin{parts}

\part[10]
$y^{\prime \prime} - 3y^{\prime}= 6e^x, \> y(0) = 0, y^{\prime}(0) = 0$

\clearpage

\part[20]
$y^{\prime \prime} - 2y^{\prime} + y = e^t \ln t$

\clearpage

\part[10]
$y^{\prime \prime} - 11y^{\prime} + 30y = -3e^{5x}$

\end{parts}

\clearpage

\question[20 ]
A mass of 1 kilogram is attached to a spring with a spring constant of 20 newtons per meter.  The system is submerged in a liquid that imparts a damping force with a magnitude equal to 8 times the velocity of the mass.  At time $t = 0$, the mass is pulled 0.5 meters below its equilibrium position and given an initial speed of 1 meter per second in the downward direction.  Find the equation of motion.

\end{questions}
\end{document}