\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, nicefrac, enumerate}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\title{Differential equations final exam - SP 17}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Final exam}}
            \hfill MAT 265, Spring 2017}
\bigskip
\bigskip

\begin{questions}

\question[10]
Find the general solution of the equation.

\begin{parts}
\part
$\dfrac{dy}{dt} = ty^2 + t$
\vspace{\stretch{2}}

\part
$y^{\prime \prime}  - 6y^{\prime} + 9y = 0$
\vspace{\stretch{3}}
\clearpage

\end{parts}

\question[12]
Initially, a tank contains 5000 liters of pure water.  A solution containing 2 kilograms of salt per liter is pumped into the tank at a rate of 15 liters per minute. A well-stirred mixture is drained from the tank at the same rate, 15 liters per minute.  How many kilograms of salt are in the tank after one hour?
\clearpage

\question[22]
A mass of 3 kilograms is connected to spring with constant 6 newtons per meter.  The system is free from damping and friction.  The mass experiences a driving force of strength
$\cos 2t$, where $t$ is time in seconds.  This force is directed upward at time $t=0$.  At the same time ($t=0$), the mass is in its equilibrium position with a velocity of 1 meter per second downward.  Find the equation of motion for the system.
\clearpage 

\question[10]
Find the Laplace transform of each function.
\begin{parts}
\part
$f(t) = t e^{-4t}$
\vspace{\stretch{2}}

\part
$g(t) = 3 \sin \dfrac{t}{2}$
\vspace{\stretch{2}}

\part
$h(t) = \begin{cases}
	3t & \mbox{if } t < 2 \\
    6 & \mbox {if } t \ge 2
\end{cases}$
\end{parts}
\vspace{\stretch{3}}
\clearpage

\question[16]
Find the inverse Laplace transform of each function.
\begin{parts}
\part
$H(s) = \dfrac{10}{s + 12}$
\vspace{\stretch{2}}

\part
$F(s) = \dfrac{s+2}{s^2+2s+5}$
\vspace{\stretch{2}}

\part
$Y(s) = \dfrac{1}{s^2+4} e^{-5 \pi s}$
\end{parts}
\vspace{\stretch{3}}
\clearpage

\question[14]
Use the power series method to find the general solution to
\begin{align*}
\left( \cos t \right) y^{\prime} + y = 0.
\end{align*}
Write the first four nonzero terms of your answer.
\clearpage

\question[16]
Find the general solution to the system.
\begin{align*}
\dfrac{dx}{dt} & = x - 8y \smallskip \\
\dfrac{dy}{dt} & = x - 3y
\end{align*}
\clearpage

\question
Find the solution to the IVP (10 points bonus)
\begin{align*}
\dfrac{dx}{dt} & = 2x + 2y && x(0) = 0 \smallskip \\
\dfrac{dy}{dt} & = x + 3y && y(0) = 1
\end{align*}
\clearpage

\end{questions}
\end{document}