\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, nicefrac}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\title{College algebra exam 3 - summer 16}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Exam 3}}
            \hfill MAT 121, Summer 2016}
\bigskip
\bigskip

\begin{questions}

\question[6]
Define the sets $A = \left\lbrace 2,4, 6, 8 \right\rbrace, B = \left\lbrace 1,2,3,4,5 \right\rbrace$, and
$C = \left\lbrace 6,8,10 \right\rbrace$.  Write the following sets.
\bigskip

\begin{parts}
\part
$B \cap C$
\vspace{\stretch{1}}

\part
$B \cap C^{\prime}$
\vspace{\stretch{1}}

\part
$A \cup B$
\vspace{\stretch{1}}

\part
$A \cap B$
\vspace{\stretch{1}}

\end{parts}

\question[6] 
In a sample of parts from a factory, there are 468 functioning parts and 78 defective ones.  If a part is chosen at random, what is the probability that it is defective?  
\vspace{\stretch{3}}

\newpage
\question[6]
First we flip a coin, and then we roll a die.
\begin{parts}
\part
What is the probability of getting tails on the coin?
\vspace{\stretch{1}}

\part
What is the probability of rolling an odd number on the die?
\vspace{\stretch{1}}

\part
What is the probability of getting tails and rolling an odd number?
\vspace{\stretch{1}}

\part
What is the probability of getting tails or rolling an odd number?
\vspace{\stretch{1}}


\end{parts}

\question[12] 
\begin{parts}
\part
A manufacturer can choose between two different computer chips.  There is a 30\% probability that chip A is defective.  There is a 5\% probability that chip B is defective.  If the company makes a machine by combining one chip of each type, find the probability that the final product contains one or more defects.
\vspace{\stretch{2}}

\part
If the company makes a chip by combining two copies of chip A, find the probability that the final product contains one or more defects.
\vspace{\stretch{3}}
\end{parts} 

\newpage

\question[4]
The names of 12 different contestants are entered into a drawing.  Winners will be chosen for first, second, and third prize.  In how many different ways can these prizes be awarded? 
\vspace{\stretch{2}}

\question[4]
From a club of 10 people, a committee of 3 people is selected to prepare a budget.  In how many different ways can the committee be chosen?
\vspace{\stretch{2}}

\question[8]
Recall that a deck of cards contains 13 diamonds, and 52 cards total.

\begin{parts}
\part
How many ways are there to choose a group of three cards from the deck?  Assume that order is not important in this problem.
\vspace{\stretch{2}}

\part
How many ways are there to choose three diamonds?
\vspace{\stretch{2}}

\part
If you choose three cards at random, what is the probability that you get three diamonds?
\vspace{\stretch{3}}
\end{parts}

\newpage
\question[20]
We have a jar with 3 blue chips and 3 white chips.  We draw two chips from the jar.  
\begin{parts}
\part
What is the probability that the first chip is blue?  
\vspace{\stretch{1}}

\part
If the first chip drawn is blue, what is the probability that the second chip is also blue?
\vspace{\stretch{1}}

\part
If the first chip is white, what is the probability that the second chip is blue?
\vspace{\stretch{1}}

\part
What is the probability of drawing two blue chips?
\vspace{\stretch{1}}

\part
What is the probability that the second chip is white?  (In this question, we have no knowledge about the color of the first chip.)

\vspace{\stretch{1}}

\part
If the second chip is white, what is the probability that the first chip was white?
\vspace{\stretch{2}}

\end{parts}


\newpage

\question[12]
The probability that a person has a certain thyroid disorder is 1.5\%.  There is a new diagnostic test for this disorder that is 90\% accurate.  If a randomly-chosen person tests positive for the disorder, what is the probability that they actually have the disease?
\vspace{\stretch{3}}

\question[6]
A bag contains one \$20 bill, two \$5 bills, and seven \$1 bills.  What is the expected value of drawing a bill from the bag?
\vspace{\stretch{4}}


\newpage

\question[16]
The cost of developing a new product is \$900,000.  There is a 35\% chance that this product will be successful.  If it does succeed, the company will receive \$2.5 million.  Would you recommend that the company develop the product?
\end{questions}
\end{document}