\documentclass[addpoints, 12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, enumitem}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\title{Quiz template}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}



\noindent {\sc {\bf {\Large Exam 3 review}}
            \hfill MAT 201, Spring 2017}
\bigskip

\bigskip
Estimate each value with linear approximation.  Use a fraction of whole numbers for your estimate.

\begin{questions}

\question
$\sqrt[3]{7}$

\question
$\dfrac{1}{\sqrt{39}}$

\question
$\arctan 0.15$

\bigskip

\question
Determine if the mean value theorem applies to the function 
\begin{align*}
	g(x) = \dfrac{x}{x^2 - 4}
\end{align*}
on the interval $[0,5]$.  If so, give the point on the graph whose existence is guaranteed by the theorem.

\question
Determine if the mean value theorem applies to the function 
\begin{align*}
	g(x) = \dfrac{10}{x + 4}
\end{align*}
on the interval $[0,5]$.  If so, give the point on the graph whose existence is guaranteed by the theorem.

\bigskip

\end{questions}

Evaluate each limit using L'Hopital's rule.

\begin{questions}
\setcounter{question}{5}

\question
$\displaystyle \lim_{x \to 0} \dfrac{e^x-1-x}{x^2}$ 

\question
$\displaystyle \lim_{x \to \infty} x^3 e^{-x^2}$

\question
$\displaystyle \lim_{x \to \pi/2^-} \left( \sec x - \tan x \right)$ 

\question
$\displaystyle \lim_{x \to 0} \left(1 - 2x \right)^{1/x}$ 

\bigskip

\end{questions}

Find each indefinite integral.

\begin{questions}
\setcounter{question}{9}

\question
$\displaystyle \int 5x^2 \, dx$

\question
$\displaystyle \int \left( \sin x + \dfrac{1}{x} \right) dx$

\question
$\displaystyle \int \left( 5 \cos (3x) + \dfrac{2x^5 - \sqrt{x}}{x} \right) dx$

\clearpage

\question
Find $f(x)$ if
\begin{align*}
f^{\prime}(x) = e^{2x} + \dfrac{20}{x^2 + 1}.
\end{align*}

\question
An experimental aircraft moves with acceleration
\begin{align*}
	a(t) = 6t + 4
\end{align*}
measured in $\textnormal{m/s}^2$.  Here $t$ denotes time in seconds after the experiment begins.  We also know that the initial velocity
of the aircraft is $v(0) = 6$ m/s, and its initial position is \newline $h(0) = 9$ m.  Find functions for the velocity and position of the aircraft at time $t$.
\end{questions}
\end{document}