\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, nicefrac, gensymb}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\newcommand{\real}{\mathbf{R}}

\title{Linear algebra exam 2}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Exam 2}}
            \hfill MAT 255, Fall 2016}
\bigskip
\bigskip

Please start each question at the top of a new page.
\bigskip

\begin{questions}

\question[7]
Find the determinant of the matrix 
$\left[ \begin{array}{ccc}
1 - x & 1 & 0 \\
1 & 1 - x & 1 \\
0 & 1 & 1 - x \\
\end{array} \right]$.

\smallskip

\question[5]
Find all values of $k$ such that the matrix 
$\left[ \begin{array}{cc}
k^2 & k \\ 1 & k \\
\end{array} \right]$
is invertible.

\question[10]
Let $H$ be the set consisting of all vectors in $\real^2$ that have the form 
$\left[ \begin{array}{c}
	2t \\ -t
\end{array} \right]$ where $t$ is a \textbf{non-negative} real number.  Is $H$ is a subspace of $\real^2$?  Justify your answer.

\question[15]
Determine if each of the following sets is a basis for $\real^2$.  Explain the reasons for your conclusions.

\begin{parts}
\part
$\left\lbrace \left[
\begin{array}{c}
5 \\ 1 
\end{array}
\right], 
\left[
\begin{array}{c}
0 \\ 0 
\end{array}
\right]
\right\rbrace$

\part
$\left\lbrace \left[
\begin{array}{c}
3 \\ -1 
\end{array}
\right], 
\left[
\begin{array}{c}
2 \\ 2 
\end{array}
\right]
\right\rbrace$

\part
$\left\lbrace \left[
\begin{array}{c}
1 \\ 0 
\end{array}
\right], 
\left[
\begin{array}{c}
1 \\ -2 
\end{array}
\right],
\left[
\begin{array}{c}
0 \\ 11 
\end{array}
\right]
\right\rbrace$

\part
$\left\lbrace \left[
\begin{array}{c}
15 \\ 5 
\end{array}
\right], 
\left[
\begin{array}{c}
-6 \\ -2 
\end{array}
\right]
\right\rbrace$
\end{parts}

\question[10]
Are the polynomials
\begin{align*}
	2 + 4t^3 && 3 + 6t + 6t^3 \\
    4 + 7t + 8t^3 && 1 + 9t^2 + 2t^3
\end{align*}
linearly independent? 

\question[18]
Find a basis set for the nullspace, columnspace, and rowspace of the matrix
\begin{equation*}
	A = \left[ \begin{array}{ccccc}
		1 & 2 & 3 & 4 \\
		6 & 13 & 20 & 27 \\
		9 & 26 & 44 & 62 \\
	\end{array} \right].
\end{equation*}
What is the rank of the matrix $A$?

\clearpage

\question[15]
Suppose that $A$ is a $4 \times 7$ matrix with four pivot columns.  What is the rank of this matrix? Give the dimensions for the nullspace, rowspace, and columnspace.  Is $\textnormal{Null}(A)$ the same as the entire space $\real^m$ for some integer $m$? Is $\textnormal{Col}(A) = \real^n$ for some integer $n$?  Does the equation
\begin{align*}
A \vec{x} = \vec{b}
\end{align*}
have a solution for every possible right-hand side vector $\vec{b}$?  Does the equation
\begin{align*}
A \vec{x} = \vec{0}
\end{align*}
have a solution other than the trivial solution $\vec{x} = \vec{0}$?

\question[20]
Let $V$ be a vector space, and let $\vec{u}$ be any vector in $V$.  Prove that the additive inverse $-\vec{u}$ is unique.  You will be graded on both the clarity of your writing and the correctness of your argument.


\end{questions}

\end{document}