\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol, nicefrac, gensymb}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\newcommand{\real}{\mathbf{R}}

\title{Linear algebra final exam fall 16}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Final exam}}
            \hfill MAT 255, Fall 2016}
\bigskip
\bigskip

\begin{questions}

\question[10]
Give precise definitions for \textbf{four} of the following five concepts.
\begin{parts}
\part
linear independence of a set of vectors
\part
the span of a set of vectors
\part
the rank of a matrix
\part
an eigenvector of a matrix
\part
a pair of orthogonal vectors
\end{parts}

\question[15]
Define the matrices $A = 
\left[ \begin{array}{cc}
2 & k \\ 0 & 3
\end{array} \right]$
and $B =
\left[ \begin{array}{ccc}
13 & 12 & 11 \\ 1 & 2 & 3
\end{array}
\right]$.

\begin{parts}
\part
Find the matrix products $AB$ and $BA$, or state that the product is undefined.

\part
Find $A^{-1}$, the inverse of the matrix $A$.
\end{parts}

\question[10]
Determine if each of the following sets is a basis for $\real^2$.  Explain the reasons for your conclusions.

\begin{parts}
\part
$\left\lbrace \left[
\begin{array}{c}
-3 \\ 19 
\end{array}
\right], 
\left[
\begin{array}{c}
12 \\ -5 
\end{array}
\right]
\right\rbrace$

\part
$\left\lbrace \left[
\begin{array}{c}
2 \\ 4 
\end{array}
\right], 
\left[
\begin{array}{c}
9 \\ 18 
\end{array}
\right]
\right\rbrace$
\end{parts}

\question[7]
One eigenvalue of the matrix $M =
\left[ \begin{array}{ccc}
1 & 2 & 1 \\ 3 & 6 & 3 \\ 4 & 8 & 4
\end{array}
\right]$
is $\lambda = 11$.  Find an eigenvector corresponding to this value.

\question[22]
Let $A =
\left[ \begin{array}{cc}
7 & -3 \\ -2 & 6
\end{array}
\right]$.  

\begin{parts}

\part
Find all eigenvalues of $A$.

\part
For every eigenvalue, find a corresponding eigenvector.

\part
Use your answers to write $A$ as the matrix product $PDP^{-1}$, where $D$ is a diagonal matrix. 

\end{parts}

\question[5]
Find the length of the vector $\vec{u} = \left[ \begin{array}{c} -1 \\ 0 \\ 5 \\ 9 \end{array} \right]$.

\question[5]
Find the distance between the vectors 
$\vec{v} = \left[ \begin{array}{c} 2 \\ 1 \\ -1  \end{array} \right]$ and 
$\vec{w} = \left[ \begin{array}{c} -1 \\ 1 \\ 3 \end{array} \right]$. 

\clearpage
\question[8]
Find a unit vector pointing in the direction of
\begin{parts}
\begin{multicols}{2}
\part 
$\vec{x} = \left[ \begin{array}{c} 5 \\ -9 \end{array} \right]$
\part
$\vec{y} = \left[ \begin{array}{c} 0 \\ 0 \\ 11 \end{array} \right]$
\end{multicols}
\end{parts}

\question[6]
Let $\alpha$ be a real number.  Give one example of a nonzero vector that is orthogonal to the vector
$\vec{v} = \left[ \begin{array}{c} 5 \\ 1 \\ \alpha  \end{array} \right]$.

\question
\begin{parts}
\part[12]
Find a basis set for the columnspace and rowspace of the matrix
\begin{equation*}
	A = \left[ \begin{array}{ccccc}
		5 & 2 & 7 \\
		17 & 5 & 22 \\
		13 & 7 & 20 \\
	\end{array} \right].
\end{equation*}

\part
10 points extra credit:
\newline Use the Gram-Schmidt process to find an orthonormal basis for each of the two spaces that you found in part (a).

\end{parts}


\end{questions}

\end{document}