\documentclass[12pt]{exam}

\setlength{\topmargin}{-.75in} \addtolength{\textheight}{2.00in}
\setlength{\oddsidemargin}{.00in} \addtolength{\textwidth}{.25in}

\usepackage{amsmath,color,graphicx, multicol}
\usepackage[inline]{asymptote}

\nofiles

\setlength{\parindent}{0in}

\pagestyle{plain}

\title{Finite exam 3 review}
\author{Wray}
\begin{document}

\begin{asydef}
//
// Global Asymptote definitions can be put here.
//
usepackage("bm");
texpreamble("\def\V#1{\bm{#1}}");
\end{asydef}

\noindent {\sc {\bf {\Large Exam 3 review problems}}
            \hfill MAT 121, Spring 2016}
\bigskip
\bigskip

\textbf{Sets}
\bigskip

Define the sets $A = \left\lbrace 3, 6, 9 ,12 \right\rbrace$ and 
$B = \left\lbrace 2, 4, 6, 8, 10, 12 \right\rbrace$, and $C = \left\lbrace -2, -1 \right\rbrace$.  Write the following sets.

\begin{questions}

\question
$A \cup B$

\question
$A \cap B$

\question
$B \cap C$

\question
$A \cap B^{\prime}$

\end{questions}

\textbf{Basic probability}
\begin{questions}
\setcounter{question}{4}
\question
Suppose we draw one card from a deck.

\begin{parts}
\part
What is the probability that we draw a black card?

\part
What is the probability that we draw a queen?

\part
What is the probability that we draw a black queen?

\part
What is the probability that we draw a card that is black or a queen?

\part
What is the probability that we draw a card that is neither black nor a queen?

\end{parts}

\question
We roll two dice.

\begin{parts}
\part
What is the probability that the first die shows an even number?

\part
What is the probability that the sum of the two dice is 10?

\part
What is the probability that the first die shows an even number and the sum of the two dice is 10?

\part
What is the probability that the first die is even or the sum of the two dice is 10?

\end{parts}

\question
A computer chip is made by connecting one circuit from factory A with a second circuit from factory B.  The circuits from factory A have a 25\% defect rate, and factory B has a 10\% defect rate.  What is the probability that a computer chip chosen at random has at least one defect?

\end{questions}


\textbf{Permutations and combinations}
\begin{questions}
\setcounter{question}{7}
\question
In a class of 9 children, 3 children will be chosen for the roles of president, vice-president, and treasurer.  In how many different ways can these roles be assigned?

\question
From a team of 10 people, we are going to choose 3 people to fly to Australia.  In how many ways can this group be chosen?

\clearpage
\question
The letters A, B, C, and D are put in a random order to make a secret code.  

\begin{parts}
\part 
How many different codes are there?

\part
How many of these codes begin with the letter A?

\part
If we choose a code at random, what is the probability that it begins with the letter B?

\part
What is the probability that a code begins with a letter other than B?

\end{parts}
\question
Five cards will be dealt from a deck to make a poker hand.

\begin{parts}
\part 
How many different five-card hands are there?

\part
How many different hands contain all clubs?

\part
How many different hands contain 3 aces and 2 kings?

\part
Find the probabilities for these two hands.  Which one is more likely?

\part
What is the probability that a hand contains at least one card that is not a club?

\end{parts}

\end{questions}

\textbf{Conditional probability and Bayes' formula}

\begin{questions}
\setcounter{question}{11}
\question
We have a jar with 1 blue chip and 4 white chips.  We draw two chips from the jar.  
\begin{parts}
\part
What is the probability that the first chip is blue?  What is the probability that the first chip is white?

\part
If the first chip drawn is blue, what is the probability that the second chip is also blue?

\part
If the first chip is white, what is the probability that the second chip is blue?

\part
What is the probability of drawing two white chips?

\part
What is the probability of drawing two blue chips?

\part
What is the probability of drawing a white chip first and then a blue chip?

\part
What is the probability that the second chip is blue?

\part
What is the probability that the second chip is white? 

\part
If the second chip is blue, what is the probability that the first chip was white?

\part
If the second chip is white, what is the probability that the first chip was blue?

\end{parts}

\question
First, we flip a coin.  If the coin shows heads, we draw a card from the deck at random.  If the coin shows tails, we pull out the queen of hearts.
\begin{parts}
\part
If the coin shows heads, what is the probability of getting a heart?

\part
If the coin shows tails, what is the probability of getting a heart?

\part
What is the probability of flipping heads and getting a heart?

\part
What is the probability of flipping tails and getting a heart?

\part
What is the probability of getting a heart?

\part
If we have a heart, what is the probability that we flipped a tail?

\part
If we have a heart, what is the probability that we flipped a head?

\end{parts}

\clearpage
\question
It is estimated that 3 out of every 10,000 people have a certain blood disease.  A new test for this disease has been developed that is 98\% accurate.  If a randomly-chosen patient gets a positive test result, what is the probability that he has the disease?

\end{questions}

\textbf{Expected value}

\begin{questions}
\setcounter{question}{14}
\question
An urn contains 10 green chips and 5 red chips.  You draw one chip.  If the chip is red, you win \$8.  If the chip is green, you pay \$5.  What is the expected value of drawing a chip?

\question 
To play a card game you must pay \$5.  You draw a card from a deck, and if it is a king you win \$50.  What is the expected value for one play of the game?

\question
The cost of developing a new product is \$2.5 million.  There is a 12\% chance that this product will be successful.  If it does succeed, the company will receive \$30 million.  Would you recommend that the company develop the product?
\end{questions}

\end{document}
