\documentclass[12pt]{exam}

\title{Worksheet template}

\usepackage{amsmath,color,graphicx}
\usepackage[inline]{asymptote}
\usepackage{gensymb, multicol, verbatim, enumitem, nicefrac}

\graphicspath{ {images/} }

\pagestyle{empty}

\setlength{\parindent}{0in}


\begin{document}

\noindent {\sc {\bf {\Large Quiz 6}}
            \hfill MAT 265, Spring 2017}
\bigskip

\noindent {\sc  {\large Name:}
             \hfill}
             
\begin{questions}

\question
One product of nuclear reactions is Plutonium-239.  After 15 years, we measure sample of Pl-239 and find that it has lost 0.043\% of its initial size.  What is the half-life of this isotope of plutonium?

\question
Suppose that a sample of charcoal contains 0.1\% of the amount of C-14 that was initially present.  Find the age of the sample.

\question
A pie is removed from an oven with an internal temperature of $300\degree$ F.  Three minutes later its temperature is $200\degree$ F.  If the temperature in the room is $70 \degree$, how long will it take the pie to reach a temperature of $75\degree$?

\question
One model for a population of animals that fluctuates with the seasons is
\begin{align*}
	\dfrac{dP}{dt} = \left( k \cos t \right) P.
\end{align*}
Find the general solution to this differential equation.

\question
Challenge: Consider a system of two connected tanks.  Tank A begins with 25 pounds of salt dissolved in 50 gallons of water, and Tank B contains 50 gallons of pure water.  Two gallons per minute of solution flow from A to B, and two gallons per minute also flow in the reverse direction, from B to A.  Three gallons per minute of pure water is pumped into Tank A, while three gallons per minute of the mixed solution is pumped out of Tank B.  Find a system of differential equations governing these mixtures.

\end{questions}

\end{document}
